---
title: "Introduction to cryptocompareR"
author: "Beniamino Sartini"
date: "2023-03-12"
output: html_document
---

```{r setup, include=FALSE}
# general setup 
knitr::opts_chunk$set(message=FALSE, echo = TRUE,  warning = FALSE, fig.align = "center", fig.pos = "H")
```

# Introduction to Cryptocompare Api

In order to install the development package, you can simply use the following commands.

```{r Installation, eval=FALSE}

# lightweight
remotes::install_github("beniamino98/cryptocompareR")
# or
devtools::install_github("beniamino98/cryptocompareR")
```

```{r Load packages}
library(dplyr)      # data manipulation and "%>%"
library(knitr)      # knit for `kable()`
library(rmdformats) # markdown templates 
library(kableExtra) # clean table outputs 
library(cryptocompareR)
```

<div style="border: 2px solid black; padding: 5px">
<a href="https://www.cryptocompare.com" target="_blank">Cryptocompare's Api</a> is one of the most complete and reliable free Api on the market. A further advantage is that it allows to request not only daily data, but also **hourly**. No other website or Api gives the access to this kind on informations on this time frame. Moreover, with a simple email registration it is possible to obtain a **free api key** that gives you the access to even more end points. 
</div>

## Symbol Price

Get the current price of any cryptocurrency given a specific currency. If the selected symbol does not trade directly into the **currency** requested, BTC will be used for conversion. If the opposite pair trades we invert it (eg.: BTC-XMR)

- allow multiple symbols (e.g.: c("BTC", "ETH"))
- allow multiple currency (e.g.: c("USDT", "BUSD"))
- allow multiple exchanges (e.g.: c("Binance", "Kraken", "Coinbase"))
- the **api key** is not requested. 


```{r Example cc_symbol_price}
kab <- cc_symbol_price(symbol = c("BTC", "ETH"), currency = c("USDT", "BUSD"), exchange = c("Binance", "Kraken", "Coinbase"), api_key = NULL)

kab %>%
  kable() %>%
  kable_classic()
```

## Historical Symbol Price (OHLCV)

Get daily historical data for **High**, **Low**, **Open**, **Close** and **Volume** of a symbol. The values are based on 00:00 GMT time. The main variables for OHLCV data are: 

- **High**: candle's highest price. 
- **Low**: candle's lowest price. 
- **Open**: candle's open price.
- **Close**: candle's close price. 
- **Volume**: candle's total volume (buy and sell) in the period.  

In addiction to **High**, **Low**, **Open**, **Close** and **Volume** we have added 3 more variables: 

- **Adj**: adjusted price computed as the mean price between the High, Low, Open and Close.
- **OC**: candle's return computed as $\frac{Close - Open}{Open}$
- **HL**: candle's return computed as $\frac{High - Low}{Low}$

### Example: Daily Data (1)

In order to obtain a time series of OHLCV data it is possible to use the function `cc_price_historical`. Specifying a specific exchange and a symbol it is possible to obtain the data from that exchange. Othewise, as default we have `exchange = NULL` and the function will return a time series computed as global mean among all the exchanges. 
In the following example we request the data of **BTCUSD** from `start = "2022-11-01"` up to `end = "2022-12-01"`. For daily data the **api key** is not requested.

```{r Example1 cc_price_historical}
# historical daily data as global mean among the exchanges 
kab_daily <- cc_price_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = NULL, currency = "USD", interval = "daily", api_key = NULL) 

kab_daily[1:5,] %>%
  kable() %>%
  kable_classic()
```

### Example: Daily Data (2)

In the following example we request the data of **BTCUSDT** from `exchange = "Binance"` from `start = "2022-11-01"` up to `end = "2022-12-01"`. For daily data the **api key** is not requested.

```{r Example2 cc_price_historical}
# historical daily data for Binance
kab_daily <- cc_price_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = "Binance", currency = "USDT", interval = "daily", api_key = NULL) 

kab_daily[1:5,] %>%
  kable() %>%
  kable_classic()
```

### Example: Hourly Data (1)

Changing the interval to *hourly* allow to retrieve the hourly candles for the pair. Also in this case the **api key** is not requested. 

```{r Example3 cc_price_historical}

kab_hourly <- cc_price_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = NULL, currency = "USD", interval = "hourly", api_key = NULL) 

kab_hourly[1:5,] %>%
  kable() %>%
  kable_classic()
```

### Example: Minutely Data (1)

Changing the interval to *minutely* allow to retrieve the minutely data for the pair only for the last 7 days. In order to get more data an api key is requested.

```{r Example4 cc_price_historical}

kab_minutely <- cc_price_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = NULL, currency = "USD", interval = "minutely", api_key = NULL) 

kab_minutely[1:5,] %>%
  kable() %>%
  kable_classic()
```


## Historical Exchange Volume

Get daily historical volume data for a symbol. The values are based on 00:00 GMT time. It is possible to obtain 3 different kind of data: 

1. Specifying a Symbol but letting `Exchange = NULL` we will obtain the volume for the symbol considering the sum of the exchanges.
2. Specifying an Exchange but letting `Symbol = NULL` we will obtain the volume for the exchange considering the sum of the symbols traded. 
3. Specifying a Symbol and an Exchange will return the volume for the symbol specified considering the specified exchange.

### Example: Symbol Volume (1)

```{r Example1 cc_exchange_historical}
# historical daily data as global mean among the exchanges 
kab_daily <- cc_exchange_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = NULL, currency = "USD", interval = "daily", api_key = NULL) 

kab_daily[1:5,] %>%
  kable() %>%
  kable_classic()
```

### Example: Exchange Volume (2)

```{r Example2 cc_exchange_historical}
# historical daily data as global mean among the exchanges 
kab_daily <- cc_exchange_historical(symbol = NULL, start = "2022-11-01", end =  "2022-12-01", exchange = "Binance", currency = "USD", interval = "daily", api_key = NULL) 

kab_daily[1:5,] %>%
  kable() %>%
  kable_classic()
```
### Example: Symbol and Exchange Volume (3)

```{r Example3 cc_exchange_historical}

# historical daily data as global mean among the exchanges 
kab_daily <- cc_exchange_historical(symbol = "BTC", start = "2022-11-01", end =  "2022-12-01", exchange = "Binance", currency = "USDT", interval = "daily", api_key = NULL) 

kab_daily[1:5,] %>%
  kable() %>%
  kable_classic()
```
