---
title: "C01-Importing-Data-with-cryptocompare"
output: 
 rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Importing Data with cryptocompare}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      fig.width = 8, 
                      fig.height = 4.5,
                      fig.align = 'center',
                      out.width='95%', 
                      dpi = 200)

```

We will now go more specifically by analyzing the various import methods available and the functions that can be used. For simplicity and speed of learning the various methods have been grouped together into a single function that can be used to communicate with the bee. Auxiliary functions were then added to display the elements that can be inserted to filter the search.

### The information available are various:
```{r}
 library(cryptocompareR)

# all exchanges available 
 all_exchanges()

# all symbols  avaliable 
 all_symbols()

```



#### 1) Stock Method and Exchange Method 

The stock and exchange methods return the financial data of a cryptocurrency. As for the stock method, it is possible to insert more than one symbol and the data will be grouped into a single tibble, it is possible to search for data by specifying one or more exchanges and if the data will be found they will be added otherwise no.
With regard to the exchange method it is possible to obtain the exchange data both for the entire market and for specific exchange or cryptocurrency.

##### gettig stocks 
The stock Data available are daily, hourly and minutly.

```{r, message = FALSE, echo=FALSE}

# A)  using cryptocompare generic function

# stock for multiple symbols in a specific interval of date 
cryptocompare( search = c("BTC","ETH", "XRP"),method = "stock", from = "2019-01-01",
               to = "2019-06-01", quiet = TRUE)

# filtering for exchange 
cryptocompare( search = c("BTC","ETH", "XRP"),method = "stock", from = "2019-01-01",
               to = "2019-06-01", exchange = "Coinbase", quiet = TRUE)


# B)  you can use the cryptocompare_stock method 
 
# stock for multiple symbols in a specific interval of date 
cryptocompare_stock( search = c("BTC","ETH", "XRP"), from = "2019-01-01",
               to = "2019-06-01", quiet = TRUE)

# filtering for exchange 
cryptocompare_stock( search = c("XRP","ETH", "BTC"),from = "2019-01-01",
               to = "2019-06-01", exchange = "Coinbase", quiet = TRUE)



```

##### gettig exchange 
The exchange Data available are daily and hourly.

```{r}

# using cryptocompare generic fun 

# market data 
cryptocompare(method = "exchange", quiet = TRUE)

# searching exchange data for some symbols 
cryptocompare(c("BTC","ETH", "XRP"),method = "exchange", quiet = TRUE)

# searching exchange data for a specific exchange 
cryptocompare(method = "exchange", exchange = c("Coinbase","Yobit"), quiet = TRUE)

# searching exchange data for a specific symbol and exchange 
cryptocompare(search = c("BTC","ETH", "XRP"),
              method = "exchange", exchange = c("Coinbase","Yobit"), quiet = TRUE)




```


#### 2) Social Method  
The social method is available only by entering an api key, so it is necessary to register to 
[cryptocompare](https://www.cryptocompare.com), and insert the key in the function.
The Social Data available are daily, hourly. 

##### getting social data 

```{r}

# social data for a symbol in an interval of dates 
# 
# cryptocompare(search = "ETH", method = "social", api_key = yourapikey, 
# from = "2019-06-01", to = "2019-11-10", quiet = T)

# social data for a group of symbols in an interval of dates 
# cryptocompare(search = c("BTC", "ETH"), method = "social", api_key = yourapikey, 
# from = "2019-06-01", to = "2019-11-10", quiet = T)
# 
# all social data availables for a group of symbols 
# cryptocompare(search = c("BTC", "ETH"), method = "social", api_key = yourapikey, quiet = T)
```

#### 3) News Method
The news method allows you to get news with titles, sources and other information on the world of cryptocurrencies. It is possible to use the method by specifying only the from and to parameters, or by filtering the data for a specific source (feeds) or for a specific category.


##### getting all news 

```{r}

# all news in an interval of dates 
cryptocompare(method = "news", from = "2019-11-01", to = "2019-11-10", quiet = T)

```

#### filter query by categorise and feeds 
```{r}

# all categories available 
 all_categories()

# all feeds avaliable 
 all_feeds()

```



##### get news by feed 

```{r}

# all news in an interval of dates searching by a specific feed   
cryptocompare(search = "yahoo", method = "news", from = "2019-06-01", to = "2019-11-10", quiet = T)

```

##### get news by categories 

```{r}
# all news in an interval of dates searching by a specific category 
cryptocompare(method = "news", categories = "BTC", from = "2019-11-01", to = "2019-11-10", quiet = T)

```

##### get news by feed and categories 

```{r}
# all news in an interval of dates searching by a specific feed  and categories 
cryptocompare(search = "yahoo", method = "news", categories = "BTC", from = "2019-06-01", to = "2019-11-10", quiet = T)
```


#### 4) General Method  

The general method allows downloading generic data.


##### accessible endpoints without an api key 
```{r}
# coin list 

cryptocompare(search = "coin", method = "general", quiet = T)


#  all exchanges info 

cryptocompare(search = "exchanges", method = "general", quiet = T)


```


##### accessible endpoints only with an api key 
```{r}

# all gambling info 

# cryptocompare(search = "gambling", method = "general", quiet = T, api_key = yourapikey)


# all wallets info 

# cryptocompare(search = "wallets", method = "general", quiet = T, api_key = yourapikey)


# all cards info 

# cryptocompare(search = "cards", method = "general", quiet = T, api_key = yourapikey)


# all mining contracts 

# cryptocompare(search = "contracts", method = "general", quiet = T, api_key = yourapikey)


# all mining companies 

# cryptocompare(search = "companies", method = "general", quiet = T,api_key = yourapikey)


# all mining equipment 

# cryptocompare(search = "equipment", method = "general", quiet = T, api_key = yourapikey)


# all mining pools

# cryptocompare(search = "pools", method = "general", quiet = T, api_key = yourapikey)



```


